The Castro AMR Simulation Code: Current and Future Developments

### 2019-09-29 astronum_2019_Castro/astronum-castro-2019.tex
more work

\begin{abstract}
We discuss 
\end{abstract}

@@

@@

MHD

Other SDC quadrature schemes / detonations

SDC multilevel + XRBs

>>>>

\begin{abstract}
We describe the \castro\ astrophysics simulation code, focusing on the
recent developments in coupling hydrodynamics and reactions and describing
upcoming developments.
\end{abstract}

@@

We've run XRB on GPUs and with SDC

@@

The development of SDC in \castro\ continues, with the current focus
on modeling detonations.  Reactions in astrophysical detonations are
especially stiff and challenging to model when the ash state reaches
nuclear statistical equilibrium.  We are exploring different
quadrature schemes for the integral in Equation~\ref{eq:sdc} to model
detonations in the SDC framework.  We are also working on extending
the SDC integration methodology to adaptive mesh refinement with
subcycling in time.

To complement the existing suite of hydrodynamics solver in \castro,
an MHD solver is under development and expected to be merged into the
main branch soon.  We will use the experiences learned with the
\castro\ hydrodynamics solver to port this solver to GPUs and fit into
the SDC framework.

All of these developments fit into our goal of modeling XRBs.
